Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-04-28 main_paper.tex
minor edit
deleted a few words in step 1 of algorithm 2. Add them back if you think
necessary.

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.
The intuition behind both procedures is straightforward. CCT show that a
local second order polynomial captures the aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
residual bootstrap.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}; Equations~\eqref{eq:2}
    and~\eqref{eq:3}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_{+}(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

>>>>

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.
The intuition behind both procedures is straightforward. CCT show that a
local second order polynomial captures the aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
residual bootstrap.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_{+}(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}
